---
title: "Koverman PS 3"
author: "Zach Koverman"
date: "2023-10-16"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

# Setup

```{r Setup}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(ggthemes)
library(broom)
library(dplyr)

options(dplyr.summarise.inform = FALSE)

set.seed(22)

setwd(paste0("/Users/zachkoverman/Desktop/School/",
      "Senior Year/ECON 487 - Data Science for Strategic Pricing/Homeworks"))
oj <- read.csv("oj.csv")
```

# Question 1

Let's focus on two variables HHLARGE ("fraction of households that are
large") and EDUC ("fraction of shoppers with advanced education").

## Part a.

What are the means and percentiles of each of these variables? HINT:
summary(oj\$EDUC)

```{r 1.a}
print("Summary Statistics of EDUC:")
summary(oj$EDUC)

print("Summary Statistics of HHLARGE:")
summary(oj$HHLARGE)
```

The mean value for EDUC is about 22.52% of shoppers have an advanced
education, with a 25th percentile of about 14.60% and a 75th percentile
of 28.44%. The mean value for HHLAARGE is about 11.6% of shoppers live
in large households, with a 25th percentile of about 9.79% and a 75th
percentile of about 13.52%.

## Part b.

Using your coefficient estimates from the regression in Q9 of the
previous problem set (if you did not include HHLARGE and EDUC, rerun the
regression with them included):

```{r 1.b}
model1b <- lm(logmove ~ log(price)*feat*brand + AGE60 + EDUC + ETHNIC + INCOME +
                HHLARGE + WORKWOM + HVAL150 + SSTRDIST + SSTRVOL + CPDIST5 + 
                CPWVOL5, oj)
summary(model1b)
```

### Part b.i.

If we move from the median value of HHLARGE to the 75th percentile (3rd
quartile), how much does log(quantity) change each week on average?
Note: if we wanted to assess the changes in levels, you'd want to take
the exponent of everything.

```{r 1.b.i}
coef_1b_hhlarge <- coef(model1b)["HHLARGE"]
summ_hhlarge_3qu <- summary(oj$HHLARGE)[5]
summ_hhlarge_med <- summary(oj$HHLARGE)[3]

change_1b_hhlarge <- coef_1b_hhlarge*(summ_hhlarge_3qu - summ_hhlarge_med)
change_1b_hhlarge
```

If we move from the median value of HHLARGE to the 75th percentile, then
log(quantity) decreases by about 2.20% each week on average.

### Part b.ii.

If we move from the median value of EDUC to the 75th percentile (3rd
quartile), how much does log(quantity) change each week on average?

```{r 1.b.ii}
coef_1b_educ <- coef(model1b)["EDUC"]
summ_educ_3qu <- summary(oj$EDUC)[5]
summ_educ_med <- summary(oj$EDUC)[3]

change_1b_educ <- coef_1b_educ*(summ_educ_3qu - summ_educ_med)
change_1b_educ
```

If we move from the median value of EDUC to the 75th percentile, then
log(quantity) increases by about 5.26% each week on average.

### Part b.iii.

Based on this analysis, which is the more important predictor of demand?

Based on this analysis, EDUC (fraction of shoppers with higher
education) is a more important predictor of demand because a change in
this variable has a larger effect on demand (log(quantity)) than a
change in HHLARGE.

## Part c.

Now let's see if these variables impact price sensitivity. Add two
interaction terms (with logprice) to the model to test this.

```{r 1.c}
model1c <- lm(logmove ~ log(price)*feat*brand + AGE60 + EDUC*log(price) + 
                ETHNIC + INCOME + HHLARGE*log(price) + WORKWOM + HVAL150 + 
                SSTRDIST + SSTRVOL + CPDIST5 + CPWVOL5, oj)
summary(model1c)
```

### Part c.i

What are the coefficients on the interaction terms?

The coefficient on the interaction term for EDUC is significant at about
3.52 and the coefficient on the interaction term for HHLARGE is
significant at about -5.35.

### Part c.ii

Does the sign of your estimates make sense based on your intuition?

Yes, the signs of these estimates make sense to me, since I would expect
orange juice to be seen as a treat that families would buy if they have
the extra money for it. Advanced education is tied to higher incomes, so
it makes sense that its coefficient is positive. On the other side,
larger families have to spend more to support more children, so I would
expect them to be less likely to have the extra money for orange juice
(which is supported by the negative sign of the coefficient).

### Part c.iii

What are the coefficient estimates on the variables EDUC and HHLARGE
that aren't part of the interaction term? How do they compare to your
regression from 1b?

The coefficient estimate for the non-interaction term EDUC variable is
now -1.90, which is decrease and change of signs from the coefficient of
0.96 in the regression in 1b. The coefficient estimate for the
non-interaction term HHLARGE variable is now 3.37, which is a large
increase and change of signs from the coefficient of -0.92 in 1b.

### Part c.iv

Similar to 2b, if we move from the median value of each variable to the
3rd quartile, how much does elasticity change? Based on this, which is
more important to price sensitivity?

```{r 1.c.iv}
coef_1c_educ <- coef(model1c)["EDUC"]
coef_1c_hhlarge <- coef(model1c)["HHLARGE"]
coef_1c_educ_it <- coef(model1c)["log(price):EDUC"]
coef_1c_hhlarge_it <- coef(model1c)["log(price):HHLARGE"]

change_1c_educ_it <- (coef_1c_educ + coef_1c_educ_it) * 
  (summ_educ_3qu - summ_educ_med)
change_1c_educ_it

change_1c_hhlarge_it <- (coef_1c_hhlarge + coef_1c_hhlarge_it) * 
  (summ_hhlarge_3qu - summ_hhlarge_med)
change_1c_hhlarge_it
```

If we move by from the median value of each variable to the 3rd quartile
now taking interaction terms as part of the regression formula,
elasticity of EDUC becomes about 0.089, while the elasticity of HHLARGE
becomes about -.047. The fraction of households with large families is
more important to price sensitivity because its elasticity is closer to
0, making it more elastic and thus is a bigger factor in making quantity
demanded sensitive to changes in price.

## Part d.

You should notice that the coefficients on EDUC and HHLARGE have flipped
sign once we include interaction terms with price. HHLARGE now appears
to be a positive demand shifter and increases price sensitivity. Explain
in words or pictures what is going on.

Now that we have an interaction term with HHLARGE tied to the
log(price), we have gained a better understanding of how family size
affects the demand for orange juice and fits into our model. Before, we
could see that areas with higher proportions of large families had lower
demand for orange juice. With the interaction term, we can see that more
large families actually increase demand for orange juice as a base
level, but these families are sensitive to changes in price and will
decrease their demand as price increases.

# Question 2

Create make a new dataframe which takes the previous week's prices as a
variable on the same line as the current week. This would enable you to
see if there is intertemporal substitution.

## Part a

There are going to be a couple of steps.First is creating a new
dataframe which is like the old one except that the week variable will
change by a single week.

### Part a.i-ii

```{r 2.a.i-ii}
oj_temp <- oj
oj_temp$week <- oj_temp$week+1
```

### Part a.iii

```{r 2.a.iii}
oj_new <- merge(oj, oj_temp, by=c("brand", "store", "week"))

# "_lag" indicates last week's value
oj_new <- oj_new %>% 
  rename("logmove_lag" = "logmove.y",
         "feat_lag" = "feat.y",
         "price_lag" = "price.y",
         "AGE60_lag" = "AGE60.y",
         "EDUC_lag" = "EDUC.y",
         "ETHNIC_lag" = "ETHNIC.y",
         "INCOME_lag" = "INCOME.y",
         "HHLARGE_lag" = "HHLARGE.y",
         "WORKWOM_lag" = "WORKWOM.y",
         "HVAL150_lag" = "HVAL150.y",
         "SSTRDIST_lag" = "SSTRDIST.y",
         "SSTRVOL_lag" = "SSTRVOL.y",
         "CPDIST5_lag" = "CPDIST5.y",
         "CPWVOL5_lag" = "CPWVOL5.y")
```

## Part b

Now run a regression with this week's log(quantity) on current and last
week's price.

```{r 2.b}
model2b <- lm(logmove.x ~ log(price.x) + log(price_lag), oj_new)
summary(model2b)
```

## Part c

What do you notice about the previous week's elasticity? Does this make
sales more or less attractive from a profit maximization perspective?
Why?

Last week's elasticity is inelastic, since the absolute value of the
coefficient is greater than 1. This makes sales more attractive from a
profit maximization perspective because it means that the previous
week's price does not have a large effective on this week's quantity
demanded, so stores should not worry about long-term effects of putting
an item on sale at the present.

# Question 3

In the last assignment you calculated the MSE on a test set. Let's
expand that code to include 5-fold cross validation.

## Part a.

Create 5 partitions of the data of equal size.

```{r 3.a}
num_rows_total <- nrow(oj_new)
num_rows_partition <- num_rows_total / 5

oj_sampled_indices <- sample(num_rows_total)
oj_shuffled <- oj_new[oj_sampled_indices, ]

labels <- rep(1:5, each = num_rows_partition, length.out = num_rows_total)
oj_split <- split(oj_shuffled, labels)

oj_split_1 <- as.data.frame(oj_split[1])
oj_split_2 <- as.data.frame(oj_split[2])
oj_split_3 <- as.data.frame(oj_split[3])
oj_split_4 <- as.data.frame(oj_split[4])
oj_split_5 <- as.data.frame(oj_split[5])

sapply(lapply(oj_split_1, unique), length)
sapply(lapply(oj_split_2, unique), length)
sapply(lapply(oj_split_3, unique), length)
sapply(lapply(oj_split_4, unique), length)
sapply(lapply(oj_split_5, unique), length)
```

## Part b.

Create 5 training datasets using 80% of the data for each one. This
could be done by "appending" the data together using rbind or via
sampling.

```{r 3.b}
oj_train_1 <- sample_frac(oj_split_1, size=.8)
oj_test_1 <- anti_join(oj_split_1, oj_train_1)
oj_train_2 <- sample_frac(oj_split_2, size=.8)
oj_test_2 <- anti_join(oj_split_2, oj_train_2)
oj_train_3 <- sample_frac(oj_split_3, size=.8)
oj_test_3 <- anti_join(oj_split_3, oj_train_3)
oj_train_4 <- sample_frac(oj_split_4, size=.8)
oj_test_4 <- anti_join(oj_split_4, oj_train_4)
oj_train_5 <- sample_frac(oj_split_5, size=.8)
oj_test_5 <- anti_join(oj_split_5, oj_train_5)
```

## Part c.

Estimate a complex model using OLS which includes price, featured,
brand, brand\*price and lagged price, all the sociodemographic variables
and interactions of EDUC and HHSIZE with price on each of the training
sets then the MSE on the test sets using the predict command.

```{r 3.c}
model3c_1 <- lm(X1.logmove.x ~ X1.price.x + X1.feat.x + X1.brand + 
                  X1.brand*X1.price.x + X1.price_lag + X1.AGE60.x + X1.EDUC.x + 
                  X1.ETHNIC.x + X1.INCOME.x + X1.HHLARGE.x + X1.WORKWOM.x + 
                  X1.HVAL150.x + X1.SSTRDIST.x + X1.SSTRVOL.x + X1.CPDIST5.x + 
                  X1.CPWVOL5.x + X1.EDUC.x*X1.price.x + X1.HHLARGE.x*X1.price.x, 
                oj_train_1)
model3c_2 <- lm(X2.logmove.x ~ X2.price.x + X2.feat.x + X2.brand + 
                  X2.brand*X2.price.x + X2.price_lag + X2.AGE60.x + X2.EDUC.x + 
                  X2.ETHNIC.x + X2.INCOME.x + X2.HHLARGE.x + X2.WORKWOM.x + 
                  X2.HVAL150.x + X2.SSTRDIST.x + X2.SSTRVOL.x + X2.CPDIST5.x + 
                  X2.CPWVOL5.x + X2.EDUC.x*X2.price.x + X2.HHLARGE.x*X2.price.x, 
                oj_train_2)
model3c_3 <- lm(X3.logmove.x ~ X3.price.x + X3.feat.x + X3.brand + 
                  X3.brand*X3.price.x + X3.price_lag + X3.AGE60.x + X3.EDUC.x + 
                  X3.ETHNIC.x + X3.INCOME.x + X3.HHLARGE.x + X3.WORKWOM.x + 
                  X3.HVAL150.x + X3.SSTRDIST.x + X3.SSTRVOL.x + X3.CPDIST5.x + 
                  X3.CPWVOL5.x + X3.EDUC.x*X3.price.x + X3.HHLARGE.x*X3.price.x, 
                oj_train_3)
model3c_4 <- lm(X4.logmove.x ~ X4.price.x + X4.feat.x + X4.brand + 
                  X4.brand*X4.price.x + X4.price_lag + X4.AGE60.x + X4.EDUC.x + 
                  X4.ETHNIC.x + X4.INCOME.x + X4.HHLARGE.x + X4.WORKWOM.x + 
                  X4.HVAL150.x + X4.SSTRDIST.x + X4.SSTRVOL.x + X4.CPDIST5.x + 
                  X4.CPWVOL5.x + X4.EDUC.x*X4.price.x + X4.HHLARGE.x*X4.price.x, 
                oj_train_4)
model3c_5 <- lm(X5.logmove.x ~ X5.price.x + X5.feat.x + X5.brand + 
                  X5.brand*X5.price.x + X5.price_lag + X5.AGE60.x + X5.EDUC.x + 
                  X5.ETHNIC.x + X5.INCOME.x + X5.HHLARGE.x + X5.WORKWOM.x + 
                  X5.HVAL150.x + X5.SSTRDIST.x + X5.SSTRVOL.x + X5.CPDIST5.x + 
                  X5.CPWVOL5.x + X5.EDUC.x*X5.price.x + X5.HHLARGE.x*X5.price.x, 
                oj_train_5)
```

### Part c.i

Calculate the MSE for the model on the test set for each fold (e.g.,
there will be five sets of model parameters and five test set MSEs with
5-fold cross validation).

```{r 3.c.i}
model3c_1_hat <- predict(model3c_1, newdata=oj_test_1)
model3c_2_hat <- predict(model3c_2, newdata=oj_test_2)
model3c_3_hat <- predict(model3c_3, newdata=oj_test_3)
model3c_4_hat <- predict(model3c_4, newdata=oj_test_4)
model3c_5_hat <- predict(model3c_5, newdata=oj_test_5)

oj_3c_1_test <- data.frame(pred = model3c_1_hat, 
                           actual = oj_test_1$X1.logmove.x)
oj_3c_2_test <- data.frame(pred = model3c_2_hat, 
                           actual = oj_test_2$X2.logmove.x)
oj_3c_3_test <- data.frame(pred = model3c_3_hat, 
                           actual = oj_test_3$X3.logmove.x)
oj_3c_4_test <- data.frame(pred = model3c_4_hat, 
                           actual = oj_test_4$X4.logmove.x)
oj_3c_5_test <- data.frame(pred = model3c_5_hat, 
                           actual = oj_test_5$X5.logmove.x)

mse_3c_1_test <- mean((oj_3c_1_test$actual - oj_3c_1_test$pred)^2)
mse_3c_2_test <- mean((oj_3c_2_test$actual - oj_3c_2_test$pred)^2)
mse_3c_3_test <- mean((oj_3c_3_test$actual - oj_3c_3_test$pred)^2)
mse_3c_4_test <- mean((oj_3c_4_test$actual - oj_3c_4_test$pred)^2)
mse_3c_5_test <- mean((oj_3c_5_test$actual - oj_3c_5_test$pred)^2)
```

### Part c.ii

Average across the MSEs to get the cross validated MSE for an OLS model
run on that particular set of features.

```{r 3.c.ii}
avg_mse_cv <- (mse_3c_1_test + mse_3c_2_test + mse_3c_3_test + mse_3c_4_test + 
                 mse_3c_5_test) / 5
print("Average test MSE across 5-fold cross validation: ")
avg_mse_cv
```

# Theoretical Questions

Assume that in addition to orange juice, you also observe demand for
bananas.

## Part a.

What regression would you run to determine if bananas and orange juice
are complements or substitutes? What is the coefficient of interest
(i.e. on what variable) that would inform you?

I would run a regression that regresses quantity of bananas purchased on
quantity of orange juice bought. If the coefficient on orange juice is
positive, that would tell me that they are complements because quantity
of bananas purchased increases as quantity of orange juice purchased
increases. If the coefficient on orange juice is negative, that would
tell me they are substitutes because the quantity of bananas purchased
decreases as the quantity of orange juice purchased increases.

## Part b.

Assume you find they are substitutes. What would the sign of the
coefficient be? Would you be more or less likely to bundle these
products if they are substitutes?

The sign of the coefficient would be negative if they were substitutes,
since that would reflect an increase in the quantity demanded of one
good corresponds to a decrease in the quantity demanded of the other.
You would be more likely to bundle these products if they are
substitutes.

### Part b.i

Explain why with an equation, figure or a sentence or two.

You would be more likely to bundle these products if they are
substitutes because that would help reduce the adverse affect on demand
that one good has on the other. The better deal would help capture sales
of the other good along with the one that the consumer is primarily
interested in.

### Part b.ii

Would the price of the bundle be less than or more than the sum of the
two independent prices? (Not a trick question; verifying you understand
bundles.)

The price of the bundle would be less than the sum of the two
independent prices, because this would convince people to buy both goods
(since it would present a better deal for the main good they want)
instead of just buying one.

## Part c.

During a sale for orange juice, should you continue to offer the bundle?
Why or why not? HINT: who is price sensitive for orange juice? Who comes
into market? Would you want to offer the bundle at a lower price than
before?

During a sale for orange juice, you should continue to offer the bundle
because the sale will hurt the demand for bananas even more, so the
bundle will be important in getting people to still buy bananas. You
would want to drp the price of the bundle as well, since otherwise
people may now find the bundle too expensive and choose to just buy
orange juice.
